\documentclass[12pt,letterpaper]{hmcpset}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{enumitem} % enumerate
% example usage of amssymb: $\mathbb{Z}$
% amsmath is loaded.

% info for header block in upper right hand corner
\name{}
\class{Math 21 - 01}
\assignment{Homework \#5}
\duedate{10/18/2019}

\begin{document}

\problemlist{Homework \#6}

\begin{problem}[1]
  \begin{enumerate}[label=(\alph*)]
  \item How many ``oddballs'' does this 15-puzzle position have?
    
    \centering
    \begin{tabular}{|c|c|c|c|}
      \hline
      3  & 14 & 15 & 9  \\ \hline
      2  & 6  & 5  & 13 \\ \hline
      8  & 7  & 12 & 4  \\ \hline
      10 & 1  & 11 & \\ \hline
    \end{tabular}
    
  \item Based on your answer to (a), determine if the 15 puzzle position is solvable.
  \end{enumerate}
\end{problem}
\begin{solution}
\end{solution}
\pagebreak

\begin{problem}[2]
  Consider the game of triangular peg solitaire with 5 rows, with 1, 2, 3, 4, and 5 holes respectively.
  It has 14 pegs and the hole in Row 1 is unoccupied.
  Same rules as traditional peg solitaire.
  Is it possible to reduce the puzzle to a single peg in the second row?
  (You may build on the strategy used in class.)
\end{problem}
\begin{solution}
\end{solution}
\pagebreak

\begin{problem}[3]
  \begin{enumerate}[label=(\alph*)]
  \item In Texas Hold'em, what is the probability that the first card of the flop is a low card (2 through 9)?
  \item Use this to estimate the probability that all 3 cards in the flop are low.
  \item Compute the exact probability that all 3 cards in the flop are low.
  \item What would be the approximate fair odds for betting that all 3 cards in the flop are low?
  \end{enumerate}
\end{problem}
\begin{solution}
\end{solution}
\pagebreak

\begin{problem}[4]
  You are dealt an 8 and 9 of diamonds in Texas Hold'em.
  The flop contains 6 of diamonds, 7 of diamonds, and Queen of hearts.
  You suspect that one of your opponents has a pair that is higher than 9s.
  \begin{enumerate}[label=(\alph*)]
  \item How many outs do you have?
  \item Estimate your probability of getting a straight or flush from the next two cards.
  \item The next card is the two of clubs.
    Now estimate your probability of getting a straight or flush on the next card.
  \item It's down to you and one other player, you have \$10 in chips remaining and your opponent bets \$10 bringing the pot to \$40.
    Should you call this bet?
  \end{enumerate}
\end{problem}
\begin{solution}
\end{solution}



\end{document}
